\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-11-19 Manuscript/manuscript.tex
minor

The rest of this paper is organized as follows. Section~\ref{sec:Data} 
describes how the data were collected. The rank-sum test, detailed 
in Section~\ref{sec:rank}, uses slightly different data from the 
generalized linear mixed-effects model (GLMM) developed in 
Section~\ref{sec:glmm}. Section~\ref{sec:Results} presents the results 
of both analyses and discusses the implications of the reaction time 
barrier. Finally, Section~\ref{sec:concludingremarks} outlines the 
paper’s impact and limitations. All data and code for our analysis 
are provided in the supplementary materials.

@@

\section{Methods} \label{sec:Methods}

@@

\subsection{GAMLSS}\label{sec:glmm}

Based on an exploratory analysis, the reaction times are adequately
modeled by a Generalized Gamma (GG) distribution with random effects in
model parameters. The GG distribution has three parameters, denoted by
$\text{GG}(\mu, \sigma, \nu)$ has density function
\[
f_Y(y \mid \mu, \sigma, \nu) = 
\frac{|\nu| \theta^\theta}{\Gamma(\theta) y} 
z^{\theta} \exp\left(-z \theta\right),
\]

for $y > 0$, $\mu > 0$, $\sigma > 0$, and $\nu \neq 0$,
where $z = \left(\frac{y}{\mu}\right)^\nu$,
$\theta = 1 / (\sigma^2 \nu^2)$.
$\Gamma(\cdot)$ denotes the Gamma function.
The GG distribution is highly flexible, encompassing several  
well-known distributions as special cases, such as the
Weibull ($\mu = \nu)$ and  Gamma $(\nu = 1)$ distributions.
Its mean is
$\mu \frac{\Gamma(\theta + 1 / \nu)}{\theta^{1 / \nu} \Gamma(\theta)}$,
provided $\theta > -1 / \nu$. Here,
$\mu$ scales the central tendency, $\sigma$ controls 
dispersion, and $\nu$ determines skewness. This parameterization allows 
the distribution to model asymmetric and heavy-tailed data effectively, making 
it particularly suitable for reaction times.
An implementation of this distribution is available from R package
\texttt{gamlss.dist} \citep{rigby2019distributions}.

>>>>

The rest of this paper is organized as follows. Section~\ref{sec:Data} 
describes the data collection and datasets used for the two
objectives. Section~\ref{sec:rank} outlines the methods for
objective~1, analyzing differences in reaction times across
competitions, including the were collected. Section~\ref{sec:gamlss}
details the methods for objective~2, the generalized additive model
for location, scale, and shape (GAMLSS) to evaluate the appropriatenes
of the 0.1-second threshold. Section~\ref{sec:Results} presents the
results of both objectives and discusses the implications.
Finally, Section~\ref{sec:concludingremarks} highlights the 
paper’s impact, limitations, and potential for future research.
All data and code for our analysis 
are provided in the supplementary materials.

@@

\section{Methods} \label{sec:methods}

@@

\subsection{GAMLSS}\label{sec:gamlss}

Based on an exploratory analysis, the reaction times are adequately
modeled by a Generalized Gamma (GG) distribution with random effects in
model parameters. The GG distribution has three parameters, denoted by
$\text{GG}(\mu, \sigma, \nu)$ has density function
\[
f_Y(y \mid \mu, \sigma, \nu) = 
\frac{|\nu| \theta^\theta z^{\theta}}{\Gamma(\theta) y} 
\exp\left(-z \theta\right),
\]
for $y > 0$, $\mu > 0$, $\sigma > 0$, and $\nu \neq 0$,
where $z = \left(\frac{y}{\mu}\right)^\nu$,
$\theta = 1 / (\sigma^2 \nu^2)$, and
$\Gamma(\cdot)$ denotes the Gamma function.
The GG distribution is highly flexible, encompassing several  
well-known distributions as special cases, such as the
Weibull ($\mu = \nu)$ and  Gamma $(\nu = 1)$ distributions.
Its mean is
\[
  \mu \frac{\Gamma(\theta + 1 / \nu)}
  {\theta^{1 / \nu} \Gamma(\theta)},
\]
provided $\theta > -1 / \nu$. Here,
$\mu$ scales the central tendency, $\sigma$ controls 
dispersion, and $\nu$ determines skewness. This parameterization allows 
the distribution to model asymmetric and heavy-tailed data effectively, making 
it particularly suitable for reaction times.
An implementation of this distribution is available from R package
\texttt{gamlss.dist} \citep{rigby2019distributions}.
